---
title: "Sleep_Report"
# author: "Nima Hamedani-Raja"
# date: "25/06/2020"
output: 
  html_document: 
    fig_height: 6
    fig_width: 10
    keep_md: yes
    # toc: yes
---

# {.tabset .tabset-fade .tabset-pills}

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r init, warning=FALSE}
source("Functions/init.R")
```

## daily_sleep {.tabset .tabset-fade .tabset-pills}

### daily_sleep {.tabset .tabset-fade .tabset-pills}

#### daily_sleep {.tabset .tabset-fade .tabset-pills}

```{r daily_sleep}
source("Functions/sleep_daily.R")

print(sleep_daily_p1)
print(sleep_daily_p2)
print(sleep_daily_p3)
```

#### Day_of_the_Week {.tabset .tabset-fade .tabset-pills}

```{r Day_of_the_Week}
print(sleep_daily_p4)
print(sleep_daily_p5)
```

### 24h_rolling {.tabset .tabset-fade .tabset-pills}

#### 24h_rolling {.tabset .tabset-fade .tabset-pills}

```{r 24h_rolling}
source("Functions/sleep_24h.R")

print(rolling_24h_p1)
print(rolling_24h_p2)
print(rolling_24h_p3)
```

#### sleep_24h_distribution {.tabset .tabset-fade .tabset-pills}

```{r sleep_24h_distribution}
source("Functions/sleep_24h_distribution.R")

print(sleep24h_distribution_p1)
print(sleep24h_distribution_p2)
print(sleep24h_distribution_p3)

```

## nap {.tabset .tabset-fade .tabset-pills}

### nap_start {.tabset .tabset-fade .tabset-pills}  

```{r nap_start}
source("nap_desctiptive.R")

print(nap_desctiptive_p1)
print(nap_desctiptive_p12)
print(nap_desctiptive_p2)
```

### nap_end {.tabset .tabset-fade .tabset-pills}  

```{r nap_end}
print(nap_desctiptive_p3)
print(nap_desctiptive_p13)
print(nap_desctiptive_p4)
```

### nap_length {.tabset .tabset-fade .tabset-pills}  

```{r nap_length}
print(nap_desctiptive_p5)
print(nap_desctiptive_p14)
print(nap_desctiptive_p6)
print(nap_desctiptive_p7)
```

### nap_start_end {.tabset .tabset-fade .tabset-pills}  
  
```{r nap_start_end}
print(nap_desctiptive_p8)
print(nap_desctiptive_p9)
print(nap_desctiptive_p10)
```

### nap_misc {.tabset .tabset-fade .tabset-pills}  

```{r nap_misc}
print(nap_desctiptive_p11)
```

## night {.tabset .tabset-fade .tabset-pills}

### night_start {.tabset .tabset-fade .tabset-pills}  

```{r night_start}
source("night_descriptive.R")

print(night_desctiptive_p1)
print(night_desctiptive_p2)
```

### night_end {.tabset .tabset-fade .tabset-pills}  

```{r night_end}
print(night_desctiptive_p3)
print(night_desctiptive_p4)
```

### night_length {.tabset .tabset-fade .tabset-pills}  

```{r night_length}
print(night_desctiptive_p5)
# print(nap_desctiptive_p14)
print(night_desctiptive_p6)
print(night_desctiptive_p7)
print(night_desctiptive_p8)
print(night_desctiptive_p9)


DF_night %>% 
  filter(Date != Sys.Date()) %>%
  mutate(recent = difftime(Sys.time(), Date, units = "days") <= 7) %>%
  # filter(night_start_time >= as.POSIXct("16:00:00", format="%H:%M:%S")) %>% 
  ggplot(aes(x = night_start_time, y = night_end_time, label = day_month)) + 
  geom_point(colour = "green") +
  geom_text(aes(colour = recent)) + 
  geom_smooth(method = "lm") + 
  theme(legend.position = "none")

DF_night %>% 
  # filter(Date != '2020-06-17') %>% 
  select(Date, night_start_time, night_end_time) %>% 
  melt(id.vars = "Date") %>% 
  ggplot(aes(x = Date, y = value, colour = variable)) + 
  geom_line() + geom_point()

DF_night %>% 
  filter(!(Date == Sys.Date() & strftime(night_start, format="%H:%M:%S") < "16:00:00")) %>%
  ggplot(aes(x = Date, y = night_length))+ 
  geom_bar(stat = "identity", fill = "blue")

prob_night %>% ggplot(aes(x = time, y = prob)) + geom_point(colour = "blue")

rbind(
  get_prob_night_start(
    DF_night, "All"),
  get_prob_night_start(
    DF_night %>% filter(difftime(Sys.time(), Date, units = "days") <= 7), "Last 7 days"),
  get_prob_night_start(
    DF_night %>% filter(difftime(Sys.time(), Date, units = "days") <= 28), "Last 28 days")) %>% 
  ggplot(aes(x = time, y = prob, colour = subset)) + geom_line()

rbind(
  get_prob_night_end(
    DF_night, "All"),
  get_prob_night_end(
    DF_night %>% filter(difftime(Sys.time(), Date, units = "days") <= 7), "Last 7 days"),
  get_prob_night_end(
    DF_night %>% filter(difftime(Sys.time(), Date, units = "days") <= 28), "Last 28 days")) %>% 
  ggplot(aes(x = time, y = prob, colour = subset)) + geom_line()

```

## Rest {.tabset .tabset-fade .tabset-pills}

### start_end_boxplots {.tabset .tabset-fade .tabset-pills}

```{r start_end_boxplots}
rbind(
  DF_night %>% 
    as.data.frame() %>% select(night_start_time,night_end_time) %>% melt() %>%
    mutate(subset = "All"),
  DF_aft %>% 
    as.data.frame() %>% select(nap_start_time,nap_end_time) %>% melt() %>%
    mutate(subset = "All"),
  DF_night %>%  
    filter(difftime(Sys.time(), Date, units = "days") <= 7) %>% 
    as.data.frame() %>% select(night_start_time,night_end_time) %>% melt() %>%
    mutate(subset = "last 7 days"),
  DF_aft %>% 
    filter(difftime(Sys.time(), Date, units = "days") <= 7) %>% 
    as.data.frame() %>% select(nap_start_time,nap_end_time) %>% melt() %>%
    mutate(subset = "last 7 days")) %>%
  ggplot(aes(x = variable , y = value, fill = subset)) + geom_boxplot()
```

### night_start v. {.tabset .tabset-fade .tabset-pills}

```{r night_start_v}
inner_join(DF_aft, DF_night, c("Date", "day_month")) %>%
  ggplot(aes(x = nap_end_time, y = night_start_time, label = day_month)) + 
  geom_point(colour = "green") +
  geom_text(colour = "red") +
  geom_smooth(method = "lm")

inner_join(DF_aft, DF_night, c("Date", "day_month")) %>%
  ggplot(aes(x = nap_length, y = night_start_time, label = day_month)) + 
  geom_point(colour = "green") +
  geom_text(colour = "red") +
  geom_smooth(method = "lm")

DF_night %>% 
  # filter(Date != Sys.Date()) %>%
  mutate(Date = Start) %>% 
  inner_join(DF_24h_summary, by = "Date") %>%
  mutate(sleep_24h = sleep_24h / 60) %>%
  filter(sleep_24h > 6) %>%
  ggplot(aes(x = sleep_24h, y= night_start_time, label = day_month)) + 
  geom_point(colour = "green") +
  geom_text(colour = "red") +
  geom_smooth(method = "lm")

inner_join(
  DF_night %>% mutate(Date = as.Date(Start)),
  DF_24h_summary %>% 
    mutate(sleep_24h = sleep_24h / 60) %>%
    filter(Date %>% strftime(format ="%H:%M:%S") == "17:00:00") %>% 
    filter(sleep_24h > 6) %>%
    mutate(Date = as.Date(Date)),
  by = "Date") %>%
  ggplot(aes(x = sleep_24h, y =night_start_time , label = day_month)) + 
  geom_point(colour = "green") +
  geom_text(colour = "red") +
  geom_smooth(method = "lm")

inner_join(
  DF_night %>% mutate(Date = as.Date(Start)),
  DF_24h_summary %>% 
    mutate(sleep_24h = sleep_24h / 60) %>%
    filter(Date %>% strftime(format ="%H:%M:%S") == "17:00:00") %>% 
    filter(sleep_24h > 6) %>%
    mutate(Date = as.Date(Date)),
  by = "Date")  %>% 
  filter(difftime(Sys.time(), Date, units = "days") <= 8) %>% 
  ggplot(aes(x = sleep_24h, y =night_start_time , label = day_month)) + 
  geom_point(colour = "green") +
  geom_text(colour = "red") +
  geom_smooth(method = "lm")
```

### NightWeaning_temp {.tabset .tabset-fade .tabset-pills}

```{r NightWeaning_temp}
source("NightWeaning_temp.R")

print(NightWeaning_test1)

print(NightWeaning_p1)
print(NightWeaning_p2)
print(NightWeaning_p1p)
print(NightWeaning_p2p)
print(NightWeaning_p3)
print(NightWeaning_p4)
print(NightWeaning_p5)
print(NightWeaning_p6)
print(NightWeaning_p7)
print(NightWeaning_p8)


inner_join(
  DF2 %>% mutate(join_value = 1),
  data.frame(time = (seq(0:(60*13))*60 - 5*60*60 - 60), join_value = 1),
  by = "join_value") %>% 
  mutate(time2 = time + 24*60*60 + as.POSIXct(Date)) %>% 
  mutate(difftime(time2, Start)) %>%
  filter(time2 >= (Start - 3600) & time2 < (End - 3600)) %>%
  group_by(time, Description) %>%
  summarise(count = n()) %>%
  ungroup() %>%
  dcast(time ~ Description, value.var = "count") %>%
  replace(is.na(.), 0) %>%
  mutate(prob_supervision = Supervision/(Supervision + Sleep + Awake)) %>%
  mutate(time = as.POSIXct(Sys.Date()) + time) %>% 
  ggplot(aes(x = time, y = prob_supervision)) + geom_line(colour = "blue")
```